---
title: "Structural Topic Modelling of Avila"
author: "Isa Lykke Hansen"
date: "21/8/2017"
output: html_document
---

```{r setup, include=FALSE}

#Setup 

knitr::opts_chunk$set(echo = TRUE)

#wd <- "~/your/filepath/here/avila/" #NB change this working directory so it points to your local Avila folder!
wd <- "~/Dropbox/IMC/avila/"
setwd(wd) 

library(pacman)
p_load(stm, #for structural topic modelling
       Rtsne, #for determining number of topics
       geometry, #for determining number of topics
       dplyr) #for data transformation

```

###Import and prepare data  
Imports the clean document term matrix and adds metadata to it  
Prepares the corpus for stm analysis
```{r}

load("data/avila_dtm") #import the clean dtm
dtm <- readCorpus(dtm, "slam") #convert the dtm to an stm-type corpus
meta <- read.csv(paste(wd, "/data/meta_data/metadata.csv", sep =''), sep = ";") #import the metadata
meta <- subset(meta, meta$format!="footnote") #make a subset of metadata that does not include footnotes
stm_data <- prepDocuments(dtm$documents, dtm$vocab, meta = meta, lower.thresh = 1) #add the metadata and remove terms that appear in only one document or less

```

###Structural Topic Modelling 
We build the models for inspection  
searchK() searches throuh different numbers of topics to find the ideal number for the models - see the output of these (lengthy) calculations in the internal > plots > stm folder
```{r}

searchK(stm_data$documents, stm_data$vocab, K = c(5, 10, 15, 20, 25, 30, 35, 40), init.type = "Spectral")

#plain model (no metadata)
model_plain <- stm(documents = stm_data$documents, vocab = stm_data$vocab,
              K = 20,
              max.em.its = 75,
              init.type = "Spectral")


#build a model where we include metadata for the format (letter, book etc.)

searchK(stm_data$documents, stm_data$vocab, K = c(5, 10, 15, 20, 25, 30, 35, 40), prevalence =~ format, data = stm_data$meta, init.type = "Spectral")

model_format <- stm(documents = stm_data$documents, vocab = stm_data$vocab,
              K = 25,
              prevalence = ~format,
              max.em.its = 500,
              data = stm_data$meta,
              init.type = "Spectral")

```

##Create models for year  
To create models for year we need to load a second dtm where we have excluded all the documents with NAs in the "year" column. 
We use the same prep-procedure as before, but create new metadata based on the old. E.g. two new columns are added; one that devides the texts into three stages of Teresas authorship and one that defines if the text was written before or after 1575. The reasoning for the division is as follows:  
- In 1560 Terese went through her second conversion (the first was in 1554) and the Inquisition made an index of illigal books (some of which Teresa had read and loved). She was 45 years old.  
- In 1575 a formal complaint about Teresas autobipgraphy, Life, was submitted to the Inquisition and her later work was written with this in mind. She was 60 years old.  

```{r}
load("data/avila_dtm_year")
dtm_year <- readCorpus(dtm_year, "slam")
meta_year <- subset(meta, !is.na(meta$year)) #exclude docs with NAs in "year"
#add columns that devide Teresas carrer into events
meta_year <- mutate(meta_year, 
                    teresa_ages = ifelse(year>1560, ifelse(year>1575, "old", "middle"),"young"),
                    before_1575 = ifelse(year<1575, "before", "after"))

stm_data_year <- prepDocuments(dtm_year$documents, dtm_year$vocab, meta = meta_year, lower.thresh = 1)

#build a model where we include metadata for the year

searchK(stm_data_year$documents, stm_data_year$vocab, K = c(5, 10, 15, 20, 25, 30, 35, 40), prevalence =~ year, data = stm_data_year$meta, init.type = "Spectral")

model_year <- stm(documents = stm_data_year$documents, vocab = stm_data_year$vocab,
              K = 25,
              prevalence = ~year,
              max.em.its = 500,
              data = stm_data_year$meta,
              init.type = "Spectral")

#build a model where we include metadata for the 3 different ages of Teresas authorship (see above for more info on this division)

searchK(stm_data_year$documents, stm_data_year$vocab, K = c(5, 10, 15, 20, 25, 30, 35, 40), prevalence =~ teresa_ages, data = stm_data_year$meta, init.type = "Spectral")

model_ages <- stm(documents = stm_data_year$documents, vocab = stm_data_year$vocab,
              K = 20,
              prevalence = ~teresa_ages,
              max.em.its = 500,
              data = stm_data_year$meta,
              init.type = "Spectral")

#build a model where we include metadata about weather the text was written before or after 1575 (see above for more info on this division)

searchK(stm_data_year$documents, stm_data_year$vocab, K = c(5, 10, 15, 20, 25, 30, 35, 40), prevalence =~ before_1575, data = stm_data_year$meta, init.type = "Spectral")

model_before <- stm(documents = stm_data_year$documents, vocab = stm_data_year$vocab,
              K = 30,
              prevalence = ~before_1575,
              max.em.its = 500,
              data = stm_data_year$meta,
              init.type = "Spectral")
```

##Model inspection  
Exploring the models with plots

```{r}

#1. PLAIN MODEL:

#different plots to toy with:

#labels of the different topics
labelTopics(model_plain, c(3,7,20))
labelTopics(model_plain, n=5)

#wordclouds:
cloud(model_format) #wordclound for all topics
cloud(model_format, topic = 23) #wordcloud for specific topic

#network plots:
mod.out.corr <- topicCorr(model_format)
plot(mod.out.corr)

#plots of topic porportions
topics_plain <- recordPlot(plot(model_plain, type = "summary")) #plot the estimated topic porportions
save(topics_plain, file = "internal/plots/stm/topics_graph_plain.rda") #save the plot to an .rda file

#2. FORMAT MODEL:

topics_format <- recordPlot(plot(model_format, type = "summary")) #plot the estimated topic porportions
save(topics_format, file = "internal/plots/stm/topics_graph_format.rda") #save the plot to an .rda file

#estimate the effect of format on topic prevalance
stm_data$meta$format <- as.factor(stm_data$meta$format)
prep_format <- estimateEffect(1:25 ~ format, model_format, meta = stm_data$meta, uncertainty = "Global")

#plot all levels of format for a specific topic
plot(prep_format, 
     "format", 
     topics = 5, 
     model = model_format, 
     printlegend = TRUE, 
     #xlab = "Time",
     xaxt = "n"
     )

#plot the difference between two topics in the format model
difference_format <- recordPlot(plot(prep_format, 
     covariate = "format", 
     topics = c(1:25),
     model = model_format, 
     method = "difference",
     cov.value1 = "letter", 
     cov.value2 = "book",
     xlab = "Books ... Letters",
     main = "Change in topic proportion from Letter to Book",
     xlim = c(-.3, .3)))
save(difference_format, file = "internal/plots/stm/difference_graph_format.rda") #save the plot to an .rda file

#we see that topic 5 is strongly associated with letters, whereas topic 23 is more strongly associated with books

plot(model_format,type = "perspectives", topics = c(5,23))

#3. YEAR MODEL:

plot(model_year, type = "summary") #plot the estimated topic porportions

#estimate the effect of year on topic prevalance
stm_data_year$meta$year <- as.factor(stm_data_year$meta$year)
prep_year <- estimateEffect(1:25 ~ year, model_year, meta = stm_data_year$meta, uncertainty = "Global")

#4. AGES MODEL:

plot(model_ages, type = "summary") #plot the estimated topic porportions

#estimate the effect of ages on topic prevalance
stm_data_year$meta$teresa_ages <- as.factor(stm_data_year$meta$teresa_ages)
prep_ages <- estimateEffect(1:20 ~ teresa_ages, model_year, meta = stm_data_year$meta, uncertainty = "Global")

#plot all levels of ages for a specific topic
plot(prep_ages, 
     "teresa_ages", 
     topics = 16, 
     model = model_ages, 
     printlegend = FALSE, 
     #xlab = "Time",
     xaxt = "n"
     )

#plot the difference between two topics in the format model
plot(prep_ages, 
     covariate = "teresa_ages", 
     topics = c(16, 5),
     model = model_ages, 
     method = "difference",
     cov.value1 = "middle", 
     cov.value2 = "old",
     xlab = "Old ... Middle",
     main = "Change in topic proportion from Middle to old age",
     xlim = c(-.3, .3))


#5. BEFORE/AFTER MODEL

topics_before <- recordPlot(plot(model_before, type = "summary")) #plot the estimated topic porportions
save(topics_before, file = "internal/plots/stm/topics_graph_before.rda") #save the plot to an .rda file

#estimate the effect of ages on topic prevalance
stm_data_year$meta$before_1575 <- as.factor(stm_data_year$meta$before_1575)
prep_before <- estimateEffect(1:30 ~ before_1575, model_before, meta = stm_data_year$meta, uncertainty = "Global")

#plot both levels of before_1575 for a specific topic
plot(prep_before, 
     "before_1575", 
     topics = 5, 
     model = model_before, 
     printlegend = FALSE,
     #xlab = "Time",
     xaxt = "n"
     )

#plot the difference between before and after 1575
difference_before <- recordPlot(plot(prep_before, 
     covariate = "before_1575", 
     topics = c(1:30),
     model = model_before, 
     method = "difference",
     cov.value1 = "after", 
     cov.value2 = "before",
     xlab = "before ... after",
     main = "Change in topic proportion from before and after 1575",
     xlim = c(-.3, .3)))
save(difference_before, file = "internal/plots/stm/difference_graph_before.rda") #save the plot to an .rda file

```

